Detecting threats of violence in YouTube comments

### 2016-03-04 submission.tex
Added to abstract

%todo: possibly a title that reflects the work better? 
\title{Detecting threats of violence in YouTube comments}

@@

\begin{abstract}
This article investigates the effect of various types of linguistic
features (lexical, morphosyntactic and semantic) for the task of
detecting threats of violence in a data set of YouTube comments. It
further examines the use of these features in combination with
different representations of the linguistic context. Our results show that ...
\end{abstract}

>>>>

%todo: possibly a title that reflects the work better? 
% Features for threat detection of user-generated text?
\title{Detecting threats of violence in YouTube comments}

@@

\begin{abstract}
This article investigates the effect of various types of linguistic
features (lexical, morphosyntactic and semantic) for the task of
detecting threats of violence in a data set of YouTube comments. It
further examines the use of these features in combination with
different representations of linguistic context and feature backoff. Our results show that combinations of lexical features outperform the use of more complex linguistic features for this task.
\end{abstract}
